### 2020-04-20 final_report/methodology.tex
compress expression in methodology intro

In the supervised learning setting, we first gather a sufficiently large
training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
to describe the behaviour of $f(x)$ across its domain.
Depending on specific model class and appropriate choice of its
hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
empirical risk with respect to $\mathcal{T}$ and a model-specific
loss function $\mathcal{L}$, where empirical risk is defined as

\begin{align}
	R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
	=\frac{1}{N}\sum_{i=1}^N
	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right).
\end{align}

>>>>

In the supervised learning setting, we first gather a sufficiently large
training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
to describe the behaviour of $f(x)$ across its domain.
Depending on specific model class and appropriate choice of its
hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
empirical risk with respect to $\mathcal{T}$ and a model-specific
loss function $\mathcal{L}$, where empirical risk is defined as
$R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
	=\frac{1}{N}\sum_{i=1}^N
	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right)$.
